\bf Visualizing Dynamic Social Network Models

### 2018-10-15 paper.Rnw
final proof-reading tweaks

\bigskip
\begin{abstract}
Stochastic actor-oriented models (SAOMs), first introduced by Snijders (1996), are a type of statistical network model for dynamic social networks. Unlike other network models, SAOMs are analytically intractable and require extensive simulation procedures for model fitting. We use model visualization techniques introduced in Wickham et al (2015) to better understand these models and their behavior. We use a three-pronged attack: (a) network visualization to view the \emph{model}, (b) exploring collections of models for parameter interpretation, and (c) delving into the fitting algorithms to gain insight into the underlying mechanisms. With the help of static and dynamic visualizations, we bring the hidden SAOM fitting processes into the foreground, with the goal of a better understanding and higher accessibility of SAOMs by social network analysts.
\end{abstract}

>>>>

\bigskip
\begin{abstract}
Stochastic actor-oriented models (SAOMs), first introduced by Snijders (1996), are statistical network models for dynamic social networks. Unlike other network models, SAOMs are analytically intractable and require extensive simulation procedures for model fitting. In this paper, we use model visualization techniques introduced in Wickham et al (2015) to better understand SAOMs and their behavior. We use a three-pronged visualization attack: (a) network visualizations to view the \emph{model}, (b) visualizations of collections of models to interpret parameters, and (c) visualizations of fitting algorithms to gain insights into the underlying mechanisms. With the help of static and dynamic visualizations, we bring the hidden SAOM fitting processes into the foreground, with the goal of a better understanding and higher accessibility of SAOMs by social network analysts.
\end{abstract}
